The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents

### 2024-02-15 main_folder/paper/The Psychology of Online Political Hostility.qmd
final version

---
title: "The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents"
author: 
  - Yiyi Feng, Yingxvan Sun
date: February 13, 2024
date-format: long
format:
  pdf:
    toc: true
    number-sections: true
thanks: "Code and data are available at: https://github.com/kqlqkqlqF/The-Psychology-of-Online-Political-Hostility.git. This paper is replicated from paper the Psychology of Online Political Hostility -- A Comprehensive, Cross-National Test of the Mismatch Hypothesis, available at : https://doi.org/10.1017/S0003055421000885."
abstract: "In contemporary society, the widespread influence of the internet and electronic technology has made the online world an indispensable part of daily human life. However, amidst this digitalization, a significant challenge has emerged: the proliferation of hostile online discussion environments.  This paper aims to replicate and analyze data from existing studies investigating the statistical disparities in individual behavior during online and offline political discussions. Additionally, it employs secondary research to explore how individuals' levels of aggressiveness correlate with the observed differences in online and offline political discourse. Our findings indicate that there is no substantial variance in hostility levels between online and offline political discussions, irrespective of an individual's level of aggression."
bibliography: referencespaper2.bib
---

@@

\newpage
```{r}
#| label: fig-tab-two
#| fig-cap: Summery of T-Test result
#| echo: false
#| message: false

>>>>

---
title: "The Psychology of Online Political Hostility -- How Aggressiveness of People Effects Their Online and Offline Comment Towards Political Incidents"
author: 
  - Yiyi Feng, Yingxvan Sun
date: February 13, 2024
date-format: long
format:
  pdf:
    toc: true
    number-sections: true
thanks: "Code and data are available at: https://github.com/kqlqkqlqF/The-Psychology-of-Online-Political-Hostility.git. This paper is replicated from paper the Psychology of Online Political Hostility -- A Comprehensive, Cross-National Test of the Mismatch Hypothesis, available at : https://doi.org/10.1017/S0003055421000885. The Reproduction DOI is at: https://doi.org/10.48152/ssrp-h9kq-h362."
abstract: "In contemporary society, the widespread influence of the internet and electronic technology has made the online world an indispensable part of daily human life. However, amidst this digitalization, a significant challenge has emerged: the proliferation of hostile online discussion environments.  This paper aims to replicate and analyze data from existing studies investigating the statistical disparities in individual behavior during online and offline political discussions. Additionally, it employs secondary research to explore how individuals' levels of aggressiveness correlate with the observed differences in online and offline political discourse. Our findings indicate that there is no substantial variance in hostility levels between online and offline political discussions, irrespective of an individual's level of aggression."
bibliography: referencespaper2.bib
---

@@

```{r}
#| label: fig-tab-two
#| fig-cap: Summery of T-Test result
#| echo: false
#| message: false
